Lake Photic Zone Temperature accross the Conterminous United States

### 2019-08-01 R/model.Rmd
B: saved a copy of RFAll to a local directory
added line to save rds
edits to figure and model code
Added rough draft of figures to the manuscript

@@

varImpPlot(RFAll)

@@

mean_run <- nla.cc %>%

  select(tmean_2m,var_sel_tmean$vars[[9]]) %>%

               ntree = 1000)

mean_run

varImpPlot(mean_run)

>>>>

nla.all<-rename(nla.all,Date=date,Average.Temperature=tmean,Longitude=longitude,
                 Thirty.Day.Average.Temperature=tmean_avg30,Elevation=elevation,
                 Latitude=latitude,Surface.Area=surface_area,
                 Shoreline.Length=shoreline_length)

@@

varImpPlot(RFAll,type=1)

# B: I'm saving a copy of the model for later use.  It is too big to github so i added it to .gitignore
saveRDS(RFAll, here::here('data/RFAll20190503.Rds'))
```

@@

### 2019-08-01 manuscript/manuscript.Rmd
Added rough draft of figures to the manuscript

![`r fig_num("varsel_fig")`](../figures/valselfig.jpg)

The final model built with the eight selected variables has a mean-squared error of 2.19 and adjusted R^2 of 0.88.  The variables ranked in order of importance were date, average temperature, longitude, 30-day average temperature, elevation, latitude, surface area, and shoreline length (Figure 3).  The partial dependency plots illustrate how the predicted photic zone temperature changes over the range of values for all predictor variables (Figure 4).

>>>>

![`r fig_num("varsel_fig")`](../figures/varselfig.jpg)

The final model built with the eight selected variables has a mean-squared error of 2.19 and adjusted R^2 of 0.88.  The variables ranked in order of importance were date, average temperature, longitude, 30-day average temperature, elevation, latitude, surface area, and shoreline length (`r fig_num("varImpPlot",caption="Variable selection plot for all variables. Shows percent increase in mean‐squared error as a function of the number of variables.", display = "cite")`).  The partial dependency plots illustrate how the predicted photic zone temperature changes over the range of values for all predictor variables (`r fig_num("partPlot",caption="Variable selection plot for all variables. Shows percent increase in mean‐squared error as a function of the number of variables.", display = "cite")`).

![`r fig_num("varImpPlot")`](../figures/varImpPlot.jpg)

![`r fig_num("partPlot")`](../figures/partPlot.jpg)
